---
title: "Introduction to Statistical Methods"
subtitle: "Academic Theme Demo"
format:
  dtslides-revealjs:
    slide-number: c/t
author:
  - name: Your Name
    orcid: 0000-0000-0000-0000
    email: alias@email.com
    affiliations: Department of Statistics
date: last-modified
---

## Overview

This presentation demonstrates the **academic** theme — a clean, neutral design suitable for any institution.

- Navy/slate color palette
- No institutional branding
- Same feature set as the UNM theme

# Data Analysis

## R Code Example

```{r}
#| echo: true

set.seed(42)
x <- rnorm(100)
y <- 2 * x + rnorm(100, sd = 0.5)
summary(lm(y ~ x))
```

## Code with Column Output {.small-slide}

```{r}
#| echo: true
#| output-location: column

df <- data.frame(
  Treatment = rep(c("A", "B", "C"), each = 4),
  Response = c(23, 25, 21, 24, 30, 32, 28, 31, 18, 20, 17, 19)
)
df |> knitr::kable()
```

# Special Features

## Emphasis Classes

- [important note]{.alert} — alert emphasis
- [highlighted]{.fg} — foreground color
- [background]{.bg} — background accent
- [key finding]{.highlight} — highlight
- [side note]{.note} — note style
- [caution]{.warning} — warning

## Callout Examples

::: {.callout-example}
This is a worked example using the academic theme.
:::

::: {.callout-question}
How does this compare to the UNM-branded version?
:::

::: {.callout-insight}
The academic theme uses a navy/slate palette for a neutral academic look.
:::

## Font Sizing Utilities

Apply size classes to a slide or a div:

:::: {.columns}
::: {.column width="50%"}
[`.larger` — 1.50em]{.larger}

[`.large` — 1.25em]{.large}

Normal text (1em)

[`.small` — 0.80em]{.small}

[`.smaller` — 0.64em]{.smaller}
:::
::: {.column width="50%"}
Code blocks scale too:

::: {.small}
```r
# .small code block
summary(lm(y ~ x))
```
:::
:::
::::

## Alignment & Buttons {.small-slide}

### Text alignment

[Left-aligned text]{.left}

[Centered text]{.center}

[Right-aligned text]{.right}

### Buttons and badges

[[Jump to Table Slide]{.button}](#table-example)

Inline labels: [v1.1.0]{.badge} [New]{.badge-secondary}

## Table Example {#table-example}

| Source    | DF  | SS   | MS   | F    |
|-----------|-----|------|------|------|
| Treatment | 2   | 312  | 156  | 52.0 |
| Error     | 9   | 27   | 3.0  |      |
| Total     | 11  | 339  |      |      |

## Scrollable Slide Demo {.scrollable}

Add `{.scrollable}` to any slide with content that intentionally exceeds the viewport. The audience can scroll through the full content.

### Full Regression Output

```{r}
#| echo: true

set.seed(42)
n <- 200
x1 <- rnorm(n)
x2 <- rnorm(n)
x3 <- rnorm(n)
y <- 3 + 2*x1 - 1.5*x2 + 0.8*x3 + rnorm(n)
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
confint(fit)
```

# Thank You

Questions?
