---
title: "Introduction to Statistical Methods"
subtitle: "Academic Theme Demo"
format:
  dtslides-revealjs:
    slide-number: c/t
author:
  - name: Your Name
    orcid: 0000-0000-0000-0000
    email: alias@email.com
    affiliations: Department of Statistics
date: last-modified
---

## Overview

This presentation demonstrates the **academic** theme — a clean, neutral design suitable for any institution.

- Navy/slate color palette
- No institutional branding
- Same feature set as the UNM theme

# Data Analysis

## R Code Example

Standard R code blocks:

````markdown
```{{r}}
#| echo: true
set.seed(42)
x <- rnorm(100)
...
```
````

```{r}
#| echo: true

set.seed(42)
x <- rnorm(100)
y <- 2 * x + rnorm(100, sd = 0.5)
summary(lm(y ~ x))
```

## Code with Column Output {.small-slide}

Use `#| output-location: column` to place output side-by-side.

```{r}
#| echo: true
#| output-location: column

df <- data.frame(
  Treatment = rep(c("A", "B", "C"), each = 4),
  Response = c(23, 25, 21, 24, 30, 32, 28, 31, 18, 20, 17, 19)
)
df |> knitr::kable()
```

# Special Features

## Emphasis Classes

Add emphasis using spans `[text]{.class}`:

- `[important note]{.alert}` $\to$ [important note]{.alert}
- `[highlighted]{.fg}` $\to$ [highlighted]{.fg}
- `[background]{.bg}` $\to$ [background]{.bg}
- `[key finding]{.highlight}` $\to$ [key finding]{.highlight}
- `[side note]{.note}` $\to$ [side note]{.note}
- `[caution]{.warning}` $\to$ [caution]{.warning}

## Callout Examples

Use divs `::: {.callout-type}` for custom boxes:

```markdown
::: {.callout-example}
This is a worked example...
:::
```

::: {.callout-example}
This is a worked example using the academic theme.
:::

::: {.callout-question}
How does this compare to the UNM-branded version?
:::

::: {.callout-insight}
The academic theme uses a navy/slate palette for a neutral academic look.
:::

## Font Sizing Utilities

Apply size classes to spans or divs:

::::: {.columns}
:::: {.column width="50%"}
- `[.larger]{.larger}` $\to$ [1.50em]{.larger}
- `[.large]{.large}` $\to$ [1.25em]{.large}
- Normal text (1em)
- `[.small]{.small}` $\to$ [0.80em]{.small}
- `[.smaller]{.smaller}` $\to$ [0.64em]{.smaller}
::::
:::: {.column width="50%"}
Code blocks scale too:

::: {.small}
```r
# .small code block
summary(lm(y ~ x))
```
:::
::::
:::::

## Alignment & Buttons {.small-slide}

### Text alignment

- `[Left]{.left}` $\to$ [Left-aligned text]{.left}
- `[Center]{.center}` $\to$ [Centered text]{.center}
- `[Right]{.right}` $\to$ [Right-aligned text]{.right}

### Buttons and badges

- Button: `[[Text]{.button}](#link)`
  - [[Jump to Table Slide]{.button}](#table-example)

- Badges: `[v1.1]{.badge}`
  - [v1.1.0]{.badge} [New]{.badge-secondary}

## Table Example {#table-example}

Standard Markdown tables:

```markdown
| Source    | DF  | SS   | MS   | F    |
|-----------|-----|------|------|------|
| Treatment | 2   | 312  | 156  | 52.0 |
```

| Source    | DF  | SS   | MS   | F    |
|-----------|-----|------|------|------|
| Treatment | 2   | 312  | 156  | 52.0 |
| Error     | 9   | 27   | 3.0  |      |
| Total     | 11  | 339  |      |      |

## Scrollable Slide Demo {.scrollable}

Add `{.scrollable}` to the slide title for long content.

`## Slide Title {.scrollable}`

### Full Regression Output

```{r}
#| echo: true

set.seed(42)
n <- 200
x1 <- rnorm(n)
x2 <- rnorm(n)
x3 <- rnorm(n)
y <- 3 + 2*x1 - 1.5*x2 + 0.8*x3 + rnorm(n)
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
confint(fit)
```

# Thank You

Questions?